% IEEE-format bibliography extracted from actual PDF papers
% Generated from real bibliographic metadata on 2026-04-20

\begin{thebibliography}{99}

\bibitem{hao2025detection}
Z.~Hao, Y.~Wang, F.~Li, G.~Ding, K.~Fan, and Y.~Gao, ``Detection of vital signs based on millimeter wave radar,'' \textit{Scientific Reports}, vol.~15, p.~28112, 2025. doi: 10.1038/s41598-025-09112-w.

\bibitem{hao2025fmcw}
Z.~Hao, Y.~Gao, Y.~Tang, Y.~Wang, K.~Fan, and F.~Li, ``FMCW-based contactless heart rate monitoring,'' \textit{Scientific Reports}, vol.~15, p.~2616, 2025. doi: 10.1038/s41598-025-86438-5.

\bibitem{zhang2026radar}
C.~Zhang, H.~Liu, Y.~Zhu, G.~Fu, X.~Chen, and D.~Yang, ``A radar vital signs detection method in complex environments,'' \textit{Scientific Reports}, vol.~16, p.~2333, 2026. doi: 10.1038/s41598-025-32042-6.

\bibitem{chen2024high}
Y.~Chen, J.~Yuan, and J.~Tang, ``A high precision vital signs detection method based on millimeter wave radar,'' \textit{Scientific Reports}, vol.~14, p.~25535, 2024. doi: 10.1038/s41598-024-77683-1.

\bibitem{sadeghi2024comprehensive}
E.~Sadeghi, K.~Skurule, A.~Chiumento, and P.~Havinga, ``Comprehensive mm-Wave FMCW Radar Dataset for Vital Sign Monitoring: Embracing Extreme Physiological Scenarios,'' \textit{arXiv preprint arXiv:2405.12659}, 2024.

\bibitem{sadeghi2025breaking}
E.~Sadeghi and P.~Havinga, ``Breaking Barriers in Health Monitoring: Multi-Scenario Vital Sign Detection Using Mm-Wave MIMO FMCW Radar,'' \textit{arXiv preprint arXiv:2508.12659}, 2025.

\bibitem{ren2024noncontact}
W.~Ren, J.~Cao, H.~Yi, K.~Hou, M.~Hu, H.~Wang, and F.~Qi, ``Noncontact Multi-Point Vital Sign Monitoring with mmWave MIMO Radar,'' \textit{IEEE Trans. Microwave Theory Tech.}, 2024, Early Access.

\bibitem{cheraghinia2024uwb}
M.~Cheraghinia, A.~Shahid, S.~Luchie, G.-J.~Godbeeke, O.~Caytan, J.~Fontaine, B.~Van Herbruggen, S.~Lemey, and E.~De Poorter, ``A Comprehensive Overview on UWB Radar: Applications, Standards, Signal Processing Techniques, Datasets, Radio Chips, Trends and Future Research Directions,'' \textit{arXiv preprint arXiv:2402.05649}, 2024.

\bibitem{bequet2022haptic}
A.~J.~B\'{e}quet, A.~R.~Hidalgo-Mu\~{n}oz, F.~Moreau, J.~Quick, and C.~Jallais, ``Subtle interactions for distress regulation: efficiency of a haptic wearable according to personality,'' \textit{Int. J. Human-Computer Studies}, vol.~167, p.~102923, 2022. doi: 10.1016/j.ijhcs.2022.102923.

\bibitem{zheng2020v2ifi}
T.~Zheng, Z.~Chen, C.~Cai, J.~Luo, and X.~Zhang, ``V$^2$iFi: in-Vehicle Vital Sign Monitoring via Compact RF Sensing,'' \textit{Proc. ACM Interact. Mob. Wearable Ubiquitous Technol.}, vol.~4, no.~2, Article~70, Jun. 2020. doi: 10.1145/3397321.

\bibitem{farouk2025noninvasive}
M.~Farouk, A.~S.~Abd El-Hameed, A.~R.~Eldamak, and D.~N.~Elsheakh, ``Noninvasive blood glucose monitoring using a dual band microwave sensor with machine learning,'' \textit{Scientific Reports}, vol.~15, p.~16271, 2025. doi: 10.1038/s41598-025-94367-6.

\bibitem{barral2024iot}
V.~Barral, T.~Dom\'{i}nguez-Bola\~{n}o, C.~J.~Escudero, and J.~A.~Garc\'{i}a-Naya, ``An IoT System for Smart Building Combining Multiple mmWave FMCW Radars Applied to People Counting,'' \textit{IEEE Internet of Things Journal}, 2024, Early Access.

\bibitem{hammouch2024uwb}
N.~Hammouch, A.~Rghioui, H.~Ammor, M.~Oubrek, and J.~Lloret, ``A low-cost UWB microwave imaging system for early-stage breast cancer detection,'' \textit{Multimedia Tools and Applications}, vol.~84, pp.~17329--17360, 2025. doi: 10.1007/s11042-024-19761-0.

\bibitem{hamza2024metamaterial}
M.~N.~Hamza, S.~Koziel, and A.~Pietrenko-Dabrowska, ``Design and experimental validation of a metamaterial-based sensor for microwave imaging in breast, lung, and brain cancer detection,'' \textit{Scientific Reports}, vol.~14, p.~16177, 2024. doi: 10.1038/s41598-024-67103-9.

\bibitem{zhang2024multimodal}
J.~Zhang, L.~Swinnen, C.~Chatzichristos, V.~Broux, R.~Proost, K.~Jansen, \textit{et al.}, ``Multimodal wearable EEG, EMG and accelerometry measurements improve the accuracy of tonic-clonic seizure detection in-hospital,'' \textit{Epilepsia}, 2024.

% NEEDS VERIFICATION - PDF was a reCAPTCHA page, not actual paper content
\bibitem{ahmed2023mmwave}
S.~Ahmed \textit{et al.}, ``Millimeter-Wave Radar and Machine Learning: A Review,'' 2023. \textit{(NEEDS VERIFICATION -- PDF file was not downloadable)}.

\bibitem{xia2025wearable}
H.~Xia, L.~Yang, B.~Jiang, Z.~Huang, and Y.~Lin, ``State-of-the-art wearable sensors for cardiovascular health: a review,'' \textit{npj Cardiovascular Health}, vol.~2, p.~53, 2025. doi: 10.1038/s44325-025-00090-6.

\bibitem{min2025wearable}
S.~Min, J.~An, J.~H.~Lee, J.~H.~Kim, D.~J.~Joe, S.~H.~Eom, C.~D.~Yoo, H.-S.~Ahn, J.-Y.~Hwang, S.~Xu, J.~A.~Rogers, and K.~J.~Lee, ``Wearable blood pressure sensors for cardiovascular monitoring and machine learning algorithms for blood pressure estimation,'' \textit{Nature Reviews Cardiology}, vol.~22, no.~9, pp.~629--648, Sep. 2025. doi: 10.1038/s41569-025-01127-0.

\bibitem{li2025evaluating}
H.~Li, M.~Zecca, and J.~Huang, ``Evaluating the Utility of Wearable Sensors for the Early Diagnosis of Parkinson Disease: Systematic Review,'' \textit{J. Med. Internet Res.}, vol.~27, p.~e69422, 2025. doi: 10.2196/69422.

\bibitem{moreau2023overview}
C.~Moreau, T.~Rouaud, D.~Grabli, I.~Benatru, P.~Remy, A.-R.~Marques, S.~Drapier, L.-L.~Mariani, E.~Roze, D.~Devos, G.~Dupoont, M.~Bru, and M.~Fabbri, ``Overview on wearable sensors for the management of Parkinson's disease,'' \textit{npj Parkinson's Disease}, vol.~9, p.~153, 2023. doi: 10.1038/s41531-023-00585-y.

\bibitem{li2023thin}
J.~Li, H.~Jia, J.~Zhou, X.~Huang, L.~Xu, S.~Jia, \textit{et al.}, ``Thin, soft, wearable system for continuous wireless monitoring of artery blood pressure,'' \textit{Nature Communications}, vol.~14, p.~5009, 2023. doi: 10.1038/s41467-023-40763-3.

\bibitem{santra2025mlrf}
A.~Santra, P.~Wang, G.~Shaker, B.~S.~Mysore, G.~Dolmans, Y.~Chen, N.~Shariati, and A.~Pandharipande, ``Machine Learning-Powered Radio Frequency Sensing: A Review,'' \textit{IEEE Sensors Journal}, 2025.

\bibitem{yang2024iradar}
H.~Yang, M.~Han, X.~Li, D.~Duan, T.~Li, and W.~Xu, ``iRadar: Synthesizing Millimeter-Waves from Wearable Inertial Inputs for Human Gesture Sensing,'' \textit{arXiv preprint arXiv:2412.15980}, 2024.

\end{thebibliography}
